---
title: "Homework 4: R Part"
subtitle: "STAT 343: Mathematical Statistics"
output:
  pdf_document:
    keep_tex: true
header-includes:
   - \usepackage{booktabs}
geometry: margin=1.5cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

\def\simiid{\stackrel{{\mbox{\text{\tiny i.i.d.}}}}{\sim}}

# Details

### How to Write Up

The written part of this assignment can be either typeset using latex or hand written.

### Grading

5% of your grade on this assignment is for turning in something legible and organized.

An additional 15% of your grade is for completion.  A quick pass will be made to ensure that you've made a reasonable attempt at all problems.

In grading these problems, an emphasis will be placed on full explanations of your thought process.  You don't need to write more than a few sentences for any given problem, but you should write complete sentences!  Understanding and explaining the reasons behind what you are doing is at least as important as solving the problems correctly.


### Collaboration

You are allowed to work with others on this assignment, but you must complete and submit your own write up.  You should not copy large blocks of code or written text from another student.

### Sources

You may refer to our text, Wikipedia, and other online sources.  All sources you refer to must be cited in the space I have provided at the end of this problem set.

## Problem 1. Adapted from Chihara and Hesterberg, Example 6.15

Let $X \sim Binomial (n,\theta)$, where $n$ is known and $\theta$ is unknown. Let's consider two potential estimators for $\theta$, $\hat{\theta}_1=\frac{X}{n}$ and $\hat{\theta}_2=\frac{X+1}{n+2}$, which adds one artificial success and one artificial failure to the real data. 

Consider the MSE of these two different estimators that you calculated in the written portion of the homework. Create graphs of the MSE as a function of $\theta$ for the following values of $n$: 16, 30, 50, 100, 200. What does changing the sample size do? 

```{r}

```


